Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-23 longoutput.tex
Start setting up Chernoff bound

\begin{theorem}
Let $H$ be a local Hamiltonian with the following properties: TODO $\mathcal{G}_{XZ}$???
\begin{itemize}
	\item has $t$ terms
	\item acts on $q$ qubits
	\item Ground state $0$...?
	\item Something something $\frac{3}{4}$?
\end{itemize}
Then, with the input, if honest is $n=O(\poly(t))$... TODO
\end{theorem}
\begin{proof}
Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$. Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(t)})$ for $i\ne1$. We now decomposite the input in this basis. We consider the Chernoff bound on... Man these variables are a pain to set up. Let's just say the result is $B$.
Let $\mathcal{I}=\mathbb{Z}_q^n$ be a collection of multi-indices.
We partition the multi-indices into three types.
$$\mathcal{I}=\mathcal{I}_1\sqcup \mathcal{I}_2\sqcup \mathcal{I}_3$$
$$\mathcal{I}_1=\set{(1,1,\ldots,1)}$$
$$\mathcal{I}_3=\set{(j_1, j_2,\ldots,j_n):\abs{\set{j_k=1}}\leq B}$$

Then we can write the input (?) as follows.
$$\alpha\ket{\phi_1^{\otimes n}}+\sum_{J\in\mathcal{I}_2}\beta_J\ket{\phi_J}+\sum_{J\in\mathcal{I}_3}\gamma_J\ket{\phi_J}$$
$$b=\sum_{J\in\mathcal{I}_2}\beta_J^2$$
$$c=\sum_{J\in\mathcal{I}_3}\gamma_J^2$$

>>>>

\begin{theorem}
Let $H$ be a local Hamiltonian with the following properties: TODO $\mathcal{G}_{XZ}$???
\begin{itemize}
	\item has $t$ terms
	\item acts on $q$ qubits
	\item Ground state $0$...?
	\item Something something $\frac{3}{4}$?
\end{itemize}
Then, with the input, if honest is $n=O(\poly(t))$... TODO
\end{theorem}
\begin{proof}
Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$. Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(t)})=p'$ for $i\ne1$. We now decomposite the input in this basis.

Fix $\frac{1}{2}<B<p'$. Consider the Chernoff bound.

Let $\mathcal{I}=\mathbb{Z}_q^n$ be the collection of possible multi-indices. That is, we decomposite the input as
$$\sum_{J\in\mathcal{I}}\alpha_J\ket{\phi_J}$$

We partition the multi-indices into three types.
$$\mathcal{I}_1=\set{(1,1,\ldots,1)}$$
$$\mathcal{I}_3=\set{(j_1, j_2,\ldots,j_n):\abs{\set{j_k=1}}\leq B}$$
$$\mathcal{I}_2=\mathcal{I}\setminus\mathcal{I}_1\setminus\mathcal{I}_3$$

Then we can write the input (?) as follows.
$$\alpha\ket{\phi_1^{\otimes n}}+\sum_{J\in\mathcal{I}_2}\beta_J\ket{\phi_J}+\sum_{J\in\mathcal{I}_3}\gamma_J\ket{\phi_J}$$
	$$b=\sum_{J\in\mathcal{I}_2}\beta_J\overline{\beta_J}$$
	$$c=\sum_{J\in\mathcal{I}_3}\gamma_J\overline{\gamma_J}$$
